---
title: ""
---

<!--Add a loading bar!-->
<script src="pace.js"></script>
<link href="pace_loadbar_loading.css" rel="stylesheet" />

<!--Create a block for title and breadcrumbs to appear on same line-->
<div style="width: 100%; display: inline-block;">
<div style="float: left;">
<h1>Rabies Incidence</h1>
</div>
<div style="float: right;">
<ol class="breadcrumb" style="background-color:white;">
  <li class="breadcrumb-item"><a href="index.html">Home</a></li>
  <li class="breadcrumb-item active">Rabies Incidence</li>
</ol>
</div>
</div>
<hr class="hr-orange">

<br>
  
<!--Begin page content!-->

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Set plot params
start_date <- as.Date("2018-01-01")
start_month <- 1
end_date <- Sys.Date()

# Find maximum number of bitten animals/bite victims for y-axis for each district
y_axis_max <- find_y_max(human_dataframe=IBCM_epi_human, animal_dataframe=IBCM_epi_animal,
                         start_month=start_month, type="epi")
```
  
### Comparison of probable exposures and cases  
  
<h5 class="text-primary"><em>This plot is in development.</em></h5><br>
  
``` {r, echo=FALSE}
epi_plot_region(human_dataframe=IBCM_epi_human, animal_dataframe=IBCM_epi_animal, 
         region="Mara", start_date=start_date, start_month=start_month,
         end_date=end_date, max_y=y_axis_max)
```

<hr class="hr-grey">
  
### Location of animal Rabies investigations  
  
The map below shows the location of suspect animal rabies cases and healthy animal bites traced in Mara Region since January 2018. Village centroids are used for all bite incidents.  
<em>Select from the dropdown menu to view data from a specific year:</em>  

```{r droplink, echo=FALSE}
# Create table
table_site <- c("html/mara_epi_map_2019.html", "html/mara_epi_map_2018.html")
names(table_site) <- c("2019", "2018")

bsselect(table_site, type = "iframe", frame_height=550, style="btn-primary", show_tick=TRUE, height=0)
```
