---
title: ""
---

<!--Add a loading bar!-->
<script src="pace.js"></script>
<link href="pace_loadbar_loading.css" rel="stylesheet" />

<!--Create a block for title and breadcrumbs to appear on same line-->
<div style="width: 100%; display: inline-block;">
<div style="float: left;">
<h1>Dog Vaccination</h1>
</div>
<div style="float: right;">
<ol class="breadcrumb" style="background-color:white;">
  <li class="breadcrumb-item"><a href="index.html">Home</a></li>
  <li class="breadcrumb-item active">Dog Vaccination</li>
</ol>
</div>
</div>
<hr class="hr-orange">

<br>
  
<!--Begin page content!-->  

### Data  
  
<h5 class="text-primary"><em>This plot is in development and currently uses randomly generated data.</em></h5>
<br>
  
```{r, echo=FALSE, warning=FALSE}
start_date <- "2018-01-01"
end_date <- Sys.Date()
dog_vac_barplot_region(dataframe=mara_dog_vacc_subset, start_date=start_date,
                       end_date=end_date)
```

<br>

<hr class="hr-grey">

### Village-level Vaccination Coverage  
  
<h5 class="text-primary"><em>This map is in development and currently uses randomly generated data.</em></h5>
<br> 

The map details villages that were vaccinated (1 or more times) in Mara Region since 2018; where villages were visited multiple times in the same year, the date and Kitongoji (sub-village) are given. Select from the dropdown menu to view a specific year:  

```{r droplink, echo=FALSE}
# Create table
table_site <- c("html/mara_vacc_map_2019.html", "html/mara_vacc_map_2018.html")
names(table_site) <- c("2019", "2018")

bsselect(table_site, type = "iframe", frame_height="550", style="btn-primary", show_tick=TRUE, height=0)
```
